\cvsection{Experience}

\begin{cventries}
  \cventry
  { Software Development Engineer 2}
  {Microsoft}
  {Hyderabad, Telangana}
  { January 2023 - Present}
  {
  \begin{cvitems}
      \item {Working on migrating services to Goverment Cloud and reducing existing tech debts.}
      \item {Working on identifying and patching multiple security vulnerabilities and making infrastructure resilient.}
      \item {Working on completion of migration of an old flow and deprecating it. Working with multiple teams and stakeholders for a smooth transition.}
  \end{cvitems}
  }
  \cventry
  {Site Reliability Engineer 2} % Job title
  {Microsoft} % Organization
  {Hyderabad, Telangana} %Location
  {February 2023 - December 2023} %Date(s)
  {
  \begin{cvitems} % Description(s) of tasks/responsibilities
  \item {Worked on migrating JSON based infrastructure definition files to C\# code to reduce duplication and configuration errors}
  \item {Worked on migrating database instances to cost effective SKU, thus reducing total infrastructure expenditure.}
  \item {Worked on migration of workloads from Azure Kubernetes Engine to Azure Kubernetes Service}
  \end{cvitems}
  }
  \cventry
  {Site Reliability Engineer} % Job title
  {Microsoft} % Organization
  {Hyderabad, Telangana} %Location
  {June 2021 - January 2023} %Date(s)
  {
  \begin{cvitems} % Description(s) of tasks/responsibilities
  \item {Worked on enhancing our support engineers' platform by integrating log pipeline to the same and adding quick filtering support to reduce overall MTTR}
  \item {Created diagnostic tools and troubleshooting guides for the support engineers to run to ease initial level of troubleshooting which resulted in about 50\% decrease in the inflow of escalations}
  \end{cvitems}
  }
  \cventry
    {DevOps Engineer (Designation: Manager)} % Job title
    {Axis Bank} % Organization
    {Mumbai, Maharastra} % Location
    {June 2018 - May 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {The first team of the organization to switch from classical deployments to CI/ CD pipelines for one click deployment.}
        \item {Deployed event-driven, micro-services based containerised application in Kubernetes orchestrator in both AWS and on-premise environment.}
        \item {Implemented monitoring, logging and alerting solutions at application and platform level using EFK stack(ElasticSearch-FluentD-Kibana) and Prometheus and Grafana.}
        \item {Implemented Istio service mesh for service discovery, authentication and security.}
        \item {Integrated security scan tools (SAST and DAST) as a part of build and deployment pipelines.}
        \item {Created extensive documentations for the platform architecture, wrote troubleshooting guides.}
        \item {Work in close coordination with the developers and other relevant teams for troubleshooting production issues.}
        \item {Plan and manage release cycles and activities for production deployments.}
        \item {Worked on setting up the disaster recovery environment for our production setup.}
          \end{cvitems}
    }
\end{cventries}
